Univalent Universes and Completness of Reversible Programs: \\ Featherweight HoTT

### 2017-03-02 upi.tex
a few more definitions

We think of a type family $P : A \to \mathcal{U}$ as a \emph{fibration} with
base space $A$, with $P(x)$ being the fiber over $x$, and with
$\Sigma_{(x:A)} P(x)$ being the \emph{total space} of the fibration, and with
first projection $\Sigma_{(x:A)} P(x) \to A$. In the figure below, the pairs
$(x,u)$ and $(y,p_*(y))$ are in the total space. A critical property of
fibrations is that a path $p : x \equiv y$ in the base space $A$ and a point $u$
in the fiber over $x$ induce a function that \emph{lifts} the path to the total
space: the lifted path starts at $(x,u)$ and ends at $(y,p_*(u))$ for some point
$p_*(u)$ in the fiber over $y$ that depends on $p$ and $u$.

@@

>>>>

\paragraph*{Type Family.} A dependent function $P : A \to \mathcal{U}$ defines a
\emph{type family}, $P(x)$ indexed by $x:A$.

\paragraph*{Transport.} Given a type family $P : A \to \mathcal{U}$, a path
$p : x \equiv y$ in $A$ induces a function $p_* : P(x) \to P(y)$ which
transports points in $P(x)$ to points in $P(y)$.

\paragraph*{Fibration.} We think of a type family $P : A \to \mathcal{U}$ as a
\emph{fibration} with base space $A$, with $P(x)$ being the fiber over $x$, and
with $\Sigma_{(x:A)} P(x)$ being the \emph{total space} of the fibration, and
with first projection $\Sigma_{(x:A)} P(x) \to A$. In the figure below, $p_*(u)$
is the transport of $u$ along $p$ and both pairs $(x,u)$ and $(y,p_*(y))$ are in
the total space. A critical property of fibrations is that a path
$p : x \equiv y$ in the base space $A$ and a point $u$ in the fiber over $x$
induce a function that \emph{lifts} the path to the total space: the lifted path
starts at $(x,u)$ and ends at $(y,p_*(u))$. A function $f : \Pi_{(x:A)} P(x)$ is
sometimes called a \emph{section} of the fibration $P$.

@@

\paragraph*{Univalent Type Family.} A type family $P : A \to \mathcal{U}$ is
\emph{univalent} if the following function is an equivalence:
\[\begin{array}{rcl}
f & : & (x \equiv y) \to (P(x) \simeq P(y)) \\
\end{array}\]
where $x,y:A$.
